### 2021-03-02 math/ia_2021/paper.tex
ia work, submitted rough draft

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
        \vspace*{4cm}
        A statistical approach to predicting a tsunami’s wave height \\
        \vspace{1cm}
        Can the height of a tsunami's wave be predicted based on the distance from and
        the magnitude of a preceding earthquake? \\
        \vspace{1cm}
        \textit{Väinö-verneri Kauppila} \\
        February 2021 \\
        \vspace{4cm}
        Word count: TBD
        \vfill
        \vspace{0.1cm}
    \end{center}
\end{titlepage}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{modelshowcase.jpeg}
    \label{fig:boat1}
\end{figure}

@@

So the relationship between the two independent variables and the wave height can
be estimated with a multivariate, polynomial regression model. We will use the Python
scikit-learn library to aid in creating this model.

\begin{figure}[h]
    \centering
    \subfloat[\centering Linear model]{{\includegraphics[width=7.5cm]{linear.png} }}
    \qquad
    \subfloat[\centering Polynomial model]{{\includegraphics[width=7.5cm]{poly.png} }}
    \caption{2 multivariate (hence the 3 dimensions) regression models}
    \label{fig:example}
\end{figure}

\dots

@@

@@

@@

All figures are generated through the use of TikZ (Tantau) and the Python library 
\verb|matplotlib|. This paper is written with the aid of the typesetting software \LaTeX. 
On a PDF viewer, the sections in the table of contents can be clicked to access that 
section.

>>>>

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
        \vspace*{4cm}
        A statistical approach to predicting a tsunami’s wave height \\
        \vspace{1cm}
        Can the height of a tsunami's wave be predicted based on the distance from and
        the magnitude of a preceding earthquake? \\
        \vspace{1cm}
        \textit{Väinö-verneri Kauppila} \\
        February 2021 \\
        \vspace{4cm}
        Word count: TBD \\
        \textit{First draft, details are missing}
        \vfill
        \vspace{0.1cm}
    \end{center}
\end{titlepage}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{modelshowcase.jpeg}
    \label{fig:boat1}
\end{figure}

@@

So the relationship between the two independent variables and the wave height can
be estimated with a multivariate, polynomial regression model. We will use the Python
scikit-learn library to aid in creating this model. \\

(\textit{Section not done, need to do more research on how the} \verb|PolynomialFeatures| 
\textit{function transforms a linear array to one fit for polynomial regression})

\begin{figure}[H]
    \centering
    \subfloat[\centering Linear model]{{\includegraphics[width=7.5cm]{linear.png} }}
    \qquad
    \subfloat[\centering Polynomial model]{{\includegraphics[width=7.5cm]{poly.png} }}
    \caption{2 multivariate (hence the 3 dimensions) regression models}
    \label{fig:example}
\end{figure}

\subsubsection{Calculating fit of the model}

@@

\textit{Conclusion and evaluation of the method are contradictory, to be corrected}

@@

\newpage
\pagenumbering{roman}

@@

All figures are generated through the use of TikZ (Tantau) and the Python library 
\verb|matplotlib|. This paper is written with the aid of the typesetting software \LaTeX. 
On a PDF viewer, the sections in the table of contents can be clicked to access that 
section. Dataset not included due to large size (\textasciitilde 28000 columns).
